MLH1 Results Outline

### 2020-02-27 doc/Results.rmd
making notes for the Q1 IFD sex difference patterns

---
title: "MLH1 Results Outline"
date: 
output:
  word_document:
    toc: yes
    toc_depth: '5'
  pdf_document: default
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
    toc_float: yes
bibliography: refs_Main_Report.bib
---

@@

first.IFD.plot_ABS <- ggplot(Curated_BivData.22, aes(y = IFD1_ABS, x= strain, color=mouse))+geom_jitter()+ggtitle("Interfocal Distances, ABS")+facet_wrap(sex~subsp, scales = "free")+ylim(c(20,160))+theme(legend.position="none") #+scale_color_manual(values=colors_of_strains)
first.IFD.plot_ABS

first.IFD.plot_PER <- ggplot(Curated_BivData.22 %>% filter(chromosomeLength < 150), aes(y = IFD1_PER, x= strain, color=chromosomeLength))+geom_jitter()+ggtitle("Interfocal Distances, PER \ncut off of chrm lengths, 150")+facet_wrap(sex~subsp, scales = "free")+ylim(c(0,1)) 
first.IFD.plot_PER
#+theme(legend.position="none")
```

@@

When the t.tests were performed within each strain, all but KAZ show (p-value = 0.3), significant sex differences in the normalized IFD measures
MSM   `r `
SKIVE  `r `
PWD  `r `
MSM  `r `
LEW  `r `
G  `r `
WSB  `r `

@@

```{r Q1.show.IFD.things, echo=FALSE}
nrm.IFD_KAZ_long <- ggplot( (Q1.IFD.long %>% filter(strain =="KAZ" ) ) , aes(y = meanIFD2CO_norm, x= sex,color=mouse))+geom_point()+ggtitle("Interfocal Distances, ABS KAZ")

@@

see the reference plots within this dir, --

@@

multiplot(kuku,bubu, cols=2)
```

>>>>

---
title: "MLH1 Results Outline"
date: 
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document: default
  word_document:
    toc: yes
    toc_depth: '5'
bibliography: refs_Main_Report.bib
---

@@

first.IFD.plot_ABS <- ggplot(Curated_BivData.22, aes(y = IFD1_ABS, x= strain, color=mouse))+geom_jitter()+ggtitle("Interfocal Distances, ABS")+facet_wrap(sex~subsp, scales = "free")+ylim(c(20,160))+theme(legend.position="none") #+scale_color_manual(values=colors_of_strains)

first.IFD.plot_PER <- ggplot(Curated_BivData.22 %>% filter(chromosomeLength < 150), aes(y = IFD1_PER, x= strain, color=chromosomeLength))+geom_jitter()+ggtitle("Interfocal Distances, PER \ncut off of chrm lengths, 150")+facet_wrap(sex~subsp, scales = "free")+ylim(c(0,1))

@@

When the t.tests were performed within each strain, all but KAZ show (p-value = 0.3), significant sex differences in the normalized IFD measures
MSM   `r Q1.IFD.PER_t.test_MSM$p.value`
SKIVE  `r Q1.IFD.PER_t.test_SKIVE$p.value`
PWD  `r Q1.IFD.PER_t.test_PWD$p.value`
MSM  `r Q1.IFD.PER_t.test_MSM$p.value`
LEW  `r Q1.IFD.PER_t.test_LEW$p.value`
G  `r Q1.IFD.PER_t.test_G$p.value`
WSB  `r Q1.IFD.PER_t.test_WSB$p.value`

@@

```{r Q1.show.IFD.things, echo=FALSE, eval=FALSE}
nrm.IFD_KAZ_long <- ggplot( (Q1.IFD.long %>% filter(strain =="KAZ" ) ) , aes(y = meanIFD2CO_norm, x= sex,color=mouse))+geom_point()+ggtitle("Interfocal Distances, ABS KAZ")

@@

nrm.IFD_sex.comp_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="KAZ" ) %>%  filter(hand.foci.count == "2") ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Normalized Interfocal Distances, ")+facet_wrap(~sex, scales = "free")+ylim(c(0,1))+theme(legend.position="none") 
```

strains where males have higher upper threshold,

G - kinda, little weak

WSB - higher upper threshold (female's have many below the 25% lower threshold, males have a few below 25% threshold)

LEW -- upper threshold looks very similar, much fewer low threshold obs in males,

PWD -- female lower threshold extends muchlower .25 (like .15?), male lower threshold very different (higher like .3) the male upper threshold is above .75

MSM -- female thresdholds, upper set around .75(to .65) lower at mostly .25, some cells(mice) have more .1 to .2 IFD observatsions.  Male upper threshold it at .75 while lower is set to .3 or .4.

SKIVE -- female upper threshold is capped at .75, lower threshold is between .25 to .3 but low rate of outliers below .25.   Male lower threshold is moved up, .4 or .35 and upper threshold moved up aprx .8

KAZ  -- female upper threshold around .75, lower threshold around .25 the distribution is quite uniform and spread out.  Male pattern; upper threshold slightly higher than .75 (.8) and lower threshold seems to extend beyond .25 -- but maybe low sampling contributes to the spread? (the spread in IFD values seems much larger for KAZ males compared to males from other strains.)

@@

#multiplot(kuku,bubu, cols=2)
```
